Job Demands-Resources model components through the lens of O*NET classifications

### 2023-02-04 Submission.Rmd
updated paper

@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits]. THE TRANSITION NEEDED HERE COULD ADDRESS RENATA'S RECOMMENDATION TO TIE THIS LITERATURE BACK INTO THE JOB-DEMANDS RESOURCES MODEL.

@@

## Summary

The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.’s (2020) conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand.

## Practical Implications

The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. ADD MORE

## Limitations and Future Directions

+	Captured only a small number of job characteristics
+	Part of that means we captured minimal “social” resources or interactions with one’s supervisor
+	Should expand on the kinds of resources employees experience, as well as stressors
+	Definition of resource, challenge, hindrance – question of distinction between resource and challenge (think about this one a little bit)

## Conclusion

@@

## Future directions

So, what can be done about the findings that people experience both? @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.

There may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

[^check]: Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion

>>>>

@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].

@@

The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.’s (2020) conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand (H2).

# Implications

Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal. There is individual difference in how employees experience the characteristics of their jobs. Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”. 
These results have implications for managers as well. The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.

# Limitations and Future Directions

As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here. First, we captured only a small number of job characteristics given the nature of our research questions. Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include. Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands. For example, we included minimal “social” resources or interactions with one’s supervisor, which the literature would suggest are important resources. Future study should explore this aspect of work. We also used the exact definitions of resource, challenge, and hindrance. It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently. It would also be interesting to consider outcomes associated with subjective ratings. 
Lastly, there may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

# Conclusion

@@

### 2023-02-04 Submission.tex
updated paper

These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

@@

Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating). In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.

@@

Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right. These categories are frequently presented in descriptions of the JD-R model and theory (cite). To answer these research questions, authors categorized items into the categories listed in the literature. For example, autonomy is frequently described as a resource. An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?''. Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 8 shows literature-derived demands (e.g., work pressure). We do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. Here, the white bars representing resources are consistently higher. ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses). describe pattern. In sum, these results provide \_\_\_ support for RQ 1 and 2.

@@

\hypertarget{summary}{%
\subsection{Summary}\label{summary}}

The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.

\hypertarget{practical-implications}{%
\subsection{Practical Implications}\label{practical-implications}}

The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. ADD MORE

\hypertarget{limitations-and-future-directions}{%
\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}

\begin{itemize}
\tightlist
\item
  Captured only a small number of job characteristics
\item
  Part of that means we captured minimal ``social'' resources or interactions with one's supervisor
\item
  Should expand on the kinds of resources employees experience, as well as stressors
\item
  Definition of resource, challenge, hindrance -- question of distinction between resource and challenge (think about this one a little bit)
\end{itemize}

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

@@

\hypertarget{future-directions}{%
\subsection{Future directions}\label{future-directions}}

So, what can be done about the findings that people experience both? J. A. LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.

There may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.\footnote{Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

>>>>

These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

@@

Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating). In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different.''

@@

Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right. These categories are frequently presented in descriptions of the JD-R model and theory (cite). To answer these research questions, authors categorized items into the categories listed in the literature. For example, autonomy is frequently described as a resource. An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?'' Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 8 shows literature-derived demands (e.g., work pressure). We do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. Here, the white bars representing resources are consistently higher. ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses). describe pattern. In sum, these results provide \_\_\_ support for RQ 1 and 2.

@@

The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).

\hypertarget{implications}{%
\section{Implications}\label{implications}}

Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal. There is individual difference in how employees experience the characteristics of their jobs. Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
These results have implications for managers as well. The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. J. A. LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.

\hypertarget{limitations-and-future-directions}{%
\section{Limitations and Future Directions}\label{limitations-and-future-directions}}

As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here. First, we captured only a small number of job characteristics given the nature of our research questions. Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include. Related to that, we intentionally worked within the O\emph{Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands. For example, we included minimal ``social'' resources or interactions with one's supervisor, which the literature would suggest are important resources. Future study should explore this aspect of work. We also used the exact definitions of resource, challenge, and hindrance. It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently. It would also be interesting to consider outcomes associated with subjective ratings.
Lastly, there may be some practical utility to pursue training interventions aimed at }how* characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.{[}\^{}check{]} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@
